\section{Machine Learning}\label{sec:machine_learning}
Machine learning is a part of the field of \ac{ai}. The focus is on extracting information from large amounts of data, with algorithms gradually improving themselves to mimic human learning~\cite{what-is-ml}.

The field of machine learning is itself divided into two main parts, \enquote{Classical learning} and \enquote{Deep learning}\cite{ml-visual-explanation}.

% https://ischoolonline.berkeley.edu/blog/what-is-machine-learning/
% https://www.ibm.com/cloud/learn/machine-learning

\subsection{Deep Learning and neural networks} % TODO: need to proof read

Deep Learning includes various techniques that use neural networks. In the simplest form, neural networks consist of different so-called nodes, which are arranged as layers\cite{neuralNet}.

The first layer, also known as the \enquote{input layer}, is the layer the input vector is applied to. If the input exceeds a certain value, the neuron is activated, i.e.\ it passes on an output.

In the next layers, which are called \enquote{hidden layers}, the outputs from all the nodes of the previous layer and a \enquote{bias layer} are computed in each node and the output is passed on. The bias layer consists of a single value that influences all nodes on a layer.

Finally, the last layer outputs the result of the computation. How strong each previous node influences the value of the current node is what the neural network is trained on.

Neural networks are particularly good at recognizing patterns in large unordered data, such as images, videos, and audio tracks. Examples of this include facial recognition or verifying hand signatures\cite{neuralNet-applications}.

\input{table-code/machine-learning/neural_network.tex}

\subsection{Classical Learning} % TODO: writing
% https://towardsdatascience.com/deep-learning-vs-classical-machine-learning-9a42c6d48aa
Algorithms in the field of classical machine learning are largely based on statistical or probabilistic methods, which originated as pattern recognition in the 1960s. It has the advantage of being a fast method that does not require much computing power compared to deep learning algorithms\cite{neuralNet}.

% https://en.wikipedia.org/wiki/Machine_learning#Approaches
% https://www.ibm.com/cloud/blog/supervised-vs-unsupervised-learning
\subsection{Supervised Learning}

\subsection{Unsupervised Learning}

\subsection{Reinforcement learning}

